### 2021-02-01 博士/毕业论文/ucasthesis/Tex/Chap_end.tex
将 end 一章翻译成中文

\chapter{END-TO-END TEMPORAL FEATURE AGGREGATION FOR SIAMESE TRACKERS}\label{chap:end}

\section{Introduction}
\label{sec:intro}
Visual object tracking is the task of estimating the state of an arbitrary target in each frame of a video sequence. 
%Recently, siamese network [] is introduced into visual tracking community, which has already been applied in many applications [].
%The key idea of siamese tracking architecture is, the target and the search image share the same feature extractor, then use correlation to tell the target position.
Recently, siamese networks have demonstrated the significant improvement on object tracking performances.
%However, sometimes the performance is bad 
However, the learned generic representation may be less discriminative because of the deteriorated object appearances in videos (Fig. \ref{fig:visulization}), such as motion blur, occlusion, \textit{etc}.
Researchers try different ways to improve the feature representation. 
For example, 
%RASNet \cite{wang2018learning} explores diverse attention mechanisms to adapt the offline learned feature representations to a specific tracking target.
SA-Siam \cite{he2018twofold} separately trains two branches to keep the heterogeneity of semantic/appearance features.
In DaSiamRPN \cite{zhu2018distractor}, a novel distractor-aware incremental learning module is designed, which can effectively transfer the general embedding to the current video domain and incrementally catch the target appearance variations  during inference.
SiamRPN++ \cite{li2019siamrpn++} introduces a simple yet effective sampling strategy to drive the siamese tracker with more powerful deep architectures.
These efforts have produced some impact and improved state-of-the-art accuracy.
%These improvements are useful.
%However, all these effort ignores a important problem: they ignore to merge the inter-frame feature during the training phase.
%One important solution is use the temporal information.
%The use of temporal information is important because, when one frame is bad, the adjusting frame can be used. While several method trying to use the temporal information, the method is naive.
%(The bug is, I cannot find any temporal information used in siamese trackers. (I cannot believe it!!! Check it again.--Checked)) For example, A use a time memory to store the appearance information. B use a simple feature average during test. C use history positional information to predict the object position in current frame. However, all these method cannot handle the temporal information during training, which lead to sub-optimal result. To solve this problem, 
However, all above siamese algorithms perform tracking based on features cropped from only the current frame, which limits the power of siamese trackers.

\begin{figure}[t]
    \centering
    \includegraphics[width=0.48\textwidth]{Img/end/visulization.pdf}
    \vspace{-0.8cm}
    \caption{A comparison of our method with SiamMask and SiamFCv2. The example frames are from the GOT-10k testing set. Our approach effectively handles poor object appearance compared to existing approaches.}
    \vspace{-0.5cm}
    \label{fig:visulization}
\end{figure}

Actually, the video has rich information about the target and such temporal information is an important basis for video understanding and tracking.
For example, in video object detection, FGFA \cite{zhu2017flow} leverages temporal coherence on feature level. It improves the per-frame features by aggregation of nearby features along the motion paths, and thus improves the video recognition accuracy.
In video object segmentation, STCNN \cite{xu2019spatiotemporal} introduces a temporal coherence module, which focuses on capturing the dynamic appearance and motion cues to provide the guidance of object segmentation.
In discriminative correlation filter-based object tracking, FlowTrack \cite{zhu2018end} focuses on making use of the rich flow information in consecutive frames to improve the feature representation and the tracking accuracy. 
However, how to utilize the temporal information in siamese trackers has not been widely studied yet.

\begin{figure*}[t]
    \centering
    \includegraphics[width=0.9\textwidth]{Img/end/net_v3.pdf}
    \vspace{-0.5cm}
    \caption{
    Overview of our two-stage SiamTFA.
    %At the first stage, a siamese FPN equipped with a temporal aggregation module provides features of the template image and the search image. Then the feature modulation module is used to merge the features and generate proposals.
    %proposals of the object given in the first-frame bounding box. 
    %At the second stage, 
    The proposal generation stage aims to generate proposals that are visually similar to the given template target. The refine stage aims to select the target from candidate proposals.}
    \label{fig:SiamTFA}
\end{figure*}

% key words: temporal modeling, model the temporal information, temporal fusion, inter-frame information, improve the feature representation, temporal aggregation, poor object appearance
In this paper, we aim to take full advantage of temporal information in siamese trackers.
%(We introduce a novel siamese tracking architecture equipped with a temporal aggregation module to make full use of inter-frame information.)
%(In this work, to deal with the issues raised above, we propose a novel tracker to aggregate features of adjacent frames by ...)
%(In this paper, we develop an end-to-end temporal aggregation module in siamese architecture to utilize both the power of siamese trackers and the inter-frame information.)
We introduce a novel siamese tracking architecture equipped with a temporal aggregation module, which improves the per-frame features by aggregating features from adjacent frames.
This temporal fusion strategy enables the siamese tracker to handle poor object appearance like motion blur, occlusion, \textit{etc}.
To achieve this, we shift the channels along the temporal dimension \cite{lin2019tsm} in the backbone of the siamese network.
Note that features of the same object are usually not spatially aligned across frames due to video motion \cite{zhu2017flow}, so the temporal shift is only performed on the residual layers \cite{lin2019tsm} to preserve the spatial feature learning capability of the siamese tracker.
Different from other temporal fusion methods \cite{tao2016siamese, gladh2016deep}, the proposed method is able to be trained end-to-end on large-scale datasets.
%The proposed temporal aggregation module is trained end-to-end in the siamese network.
%(This module enables our module to be trained end-to-end on large-scale datasets.)
Additionally, our temporal fusion method is easy to implement, without changing the siamese tracking architecture or using optical flow \cite{zhu2018end}.

%improve the generalization ability on bad object.
%Our insight is that, if we only rely on the traditional training method, the bad image in the training data will be over wheeled by the easy cases. So the tracker shows bad performance when meeting with bad image during testing. To solve this problem, we take advantage of the recent progress in adversarial learning to increase the robustness of object features.
%Our method employs adversarial dropout to increase the robustness of object features. 
%注意，由于该模块在文章中占据次要位置，所以不应该写目前方法存在的缺点，而应该直接写用了这个模块后起到的作用。
%感觉概括性的优点不太好想，所以可以多些几句实现细节。这就要求我们弄懂代码原理。
To improve the robustness of target features, we further incorporate an adversarial dropout \cite{park2018adversarial} module in the siamese tracking network.
% add adversarial dropout to enforce the tracker to learn difficult cases. 
% (We further propose a adversarial training module to enforce the tracker to learn difficult cases. The motivation is that ... This is achieved by computing the adversarial masks based on diversity maximum. This simple form of feature selection improves the discrimination power of the tracker.)
%Specifically, we calculate the diversity of two dropouts, and make the loss max to learn the difficult dropout mask.
Specifically, we first predict adversarial dropout masks based on divergence maximum.
Then, we aim to minimize the divergence between the randomly dropped features and the adversarially dropped features.
%The effect of this module can be interpreted from both the dropout and from the adversarial training perspectives.
This module has both the advantages of dropout and adversarial training: the dropout makes our siamese network randomly disconnects neural units during training to prevent the co-adaptation of target features and the adversarial training enforces our tracker to learn difficult cases.

@@

\section{The proposed Method}
\label{sec:method}
%应该提及我们的跟踪器的损失函数包括：对抗性损失，加上常规跟踪损失。
%In this section, we will introduce the proposed tracking method, SiamTFA (Fig. \ref{fig:SiamTFA}). 
%The main feature is:
%(1) A strong backbone. Use FPN and new-proposed feature modulation.
%(2) Equipped with 2 useful module: temporal aggregation module and adversarial dropout module to improve the robustness of features.
%In the following, three sub-section will be introduced: (1) Overview of tracking (2) Temporal aggregation module (3) Adversarial dropout module.
%网络结构怎么描述？可以参考ATOM。
%Our SiamTFA bases on a strong feature extractor -- FPN.
%We insert our temporal aggregation module in the backbone. Details of this module will be introduced at sec 3.2.
%Be robust to object size.
%FPN: handle different object size.
%modulator vector: handle different template object size.
%xcorr depth-wise: stage1 merge.
%element wise product: stage2 merge
% 介绍输入
%The input of the network is ... We use notations ... to denote ..., respectively. ... has a size of ...
%SiamTFA is composed of ... and ...
%Inspired by the great success of siamese trackers \cite{li2019siamrpn++, wang2019fast}, we also construct our SiamTFA based on the siamese architecture.
In this section, we will introduce the proposed siamese architecture-based tracking method, namely SiamTFA (Fig. \ref{fig:SiamTFA}), which is inspired by the great success of siamese trackers \cite{li2019siamrpn++, wang2019fast}.
Specifically, SiamTFA takes an image pair as input, comprising a template image and a search image. The template image is the image patch cropped from the initial frame according to ground truth bounding box. The search image is one whole frame in the remaining of the video. Both inputs share the same feature extractor and parameters.
Inspired by the success of the two stage detection paradigm \cite{ren2015faster}, our siamese tracker is also a two stage method. The first stage aims to generate proposals that are visually similar to the given template target. In this stage, we introduce a temporal aggregation module
%(Fig. \ref{fig:TSM}) 
to enhance the temporal information (Sec. \ref{sec:stage1}). The second stage aims to
identify the target from candidate proposals.
% select the target from candidate proposals. 
In this stage, we insert an adversarial dropout module to learn more robust features (Sec. \ref{sec:stage2}).

\subsection{Temporal aggregation module}
\label{sec:stage1}
% Note that 'stage1' and 'stage2' is a local term. You should introduce the global architecture which includes 'stage1' and 'stage2' first.
% You need to say something about ‘siamese' and the 'input'.
The proposal generation stage consists of 3 components: (1) feature extractor, (2) temporal aggregation module, and (3) feature modulation module.
% 需要综述三个模块在stage1中的作用。
The feature extractor generates the search features and the template feature for the search image and the template image, respectively. The temporal aggregation module is integrated into the feature extractor to utilize the temporal information. The feature modulation module merge the search features and the template feature to recognize the candidate targets.

\textbf{Feature extractor} To deal with the scale change of the target, we use Res50-FPN \cite{lin2017feature} as our feature extractor.
% You need to describe FPN here. What is FPN?
\textbf{F}eature \textbf{P}yramid \textbf{N}etwork (FPN) exploits the inherent multi-scale,  pyramidal hierarchy of deep convolutional networks to construct feature pyramids with marginal extra cost. 
Our siamese FPN takes a template image and a search image as input. For the search image, the FPN outputs proportionally sized feature maps at multiple levels, in a fully convolutional fashion.
%The input of the feature extractor is an image pair consists of a template image and a search image. The search image is resized to min size 800. The template is cropped according to ground truth bounding box and resized into 400*400. According to the siamese architecture, the template/search image share the same parameters. 
%For the search image, we got 5 different features and they have strides of \{4, 8, 16, 32, 64\} pixels with respect to the input image. For template branch, we use the last layer of FPN with size 7*7. 
We denote the output for the search image as $F_{x} = \{f_{x}^i\}_{i=1:5}$, and note that they have strides of \{4, 8, 16, 32, 64\} pixels with respect to the input search image.
For the template image, we use the last stage of the FPN output as the template feature with a spatial size of $7 \times 7$.
%Different from traditional trackers, our template/search features have temporal information. The reason is because we insert the temporal shift module into the backbone, which will be introduced next.

\textbf{Temporal aggregation module}
%Different from traditional trackers, we use the rich information about the same object instance by 
Most popular siamese trackers \cite{li2019siamrpn++, wang2019fast} use the still image to make prediction. % However, tracking on single frame generates unstable results and fails when appearance is pool \cite{zhu2017flow}. 
This limits the ability of these siamese trackers.
On one hand, tracking on single frame generates unstable results and fails when appearance is poor (Fig. \ref{fig:visulization}); on the other hand, 
temporal adjacent frames can provide more information about the target.
%the video has rich information about the target. 
So we aim to improve the per-frame features by aggregating features of adjacent frames.
Specifically, we insert a temporal aggregation module into the last stage of the feature extractor. 
% We have to cite TSM, because we use this idea.
To model temporal information, the images in one batch are several adjacent frames in the same video and are sorted by time, so we can regard the batch dimension as the time dimension. Assume the feature map at the last stage of the feature extractor is $f \in \mathbb R ^ {T \times C \times H \times W}$.
For each time $t \leq T$, we first split feature $f^t \in \mathbb R ^ {C \times H \times W}$ into 3 parts along the channel dimension: $f_{1:K}^t \in \mathbb R ^ {K \times H \times W}$, $f_{(K+1):2K}^t \in \mathbb R ^ {K \times H \times W}$, and $f_{(2K+1):C}^t \in \mathbb R ^ {(C-2K) \times H \times W}$.
Then we shifts the channels along the temporal dimension following \cite{lin2019tsm}:
% Then The aggregated function at time $t$ is:
\begin{equation}
    f_{agg}^t = \mathcal{C}(f_{{1:K}}^{t-1}, f_{(K+1):2K}^{t+1}, f_{(2K+1):C}^{t}),
\end{equation}
where $\mathcal{C}(\cdot)$ is the concatenation operation. According to \cite{lin2019tsm}, the shift operation is only performed at the residual layer to preserve the spatial feature learning capability of the siamese tracker.
Note that the aggregated feature $f_{agg}^t$ has the same shape with $f^t$, so we can insert this module into the backbone directly, without the need to change other part of the network.
What's more, this operation only needs to do data movement, so it is computationally free and can be trained end-to-end.
% Say the effect of this module.
%After performing such channel fusion, rich target information in adjacent frames can be aggregated into the current frame. For example, if the current frame is blurred, target information that is not blurred in adjacent frames can be used.

@@

\textbf{Feature modulation module} After getting the template feature $f_{z}$ and the search feature pyramid $F_{x} = \{f_{x}^i\}_{i=1:5}$, they are modulated to generate target-specific features.
Specifically, The modulation vector $f_{avg}$ is generated from $f_{z}$ using global average pooling, which carries the target-specific appearance information. 
%The search feature pyramid is $F = \{f_1, f_2, f_3\}$. 
%For $f_{x}^{i} \in F_{x}$, t
The modulated feature pyramid $F_{mod} = \{f_{mod}^i\}_{i=1:5}$ is generated as follows:
\begin{equation}
    f_{mod}^i = \mathcal{M}(f_{avg}, f^i_x),
\end{equation}
where $\mathcal M(\cdot)$ is the depth-wise correlation \cite{li2019siamrpn++}.
%So we get the modulated feature pyramid $F_{mod} = \{f_{mod}^i\}_{i=1:5}$. 
%Then we predict proposals on $F_{mod}$.
Each modulated feature map is fed into two sibling fully-connected layers---a box-regression layer with channel dimension 4$k$, and a box classification layer with channel dimension 2$k$, where $k$ is the number of maximum possible proposals for each location.
% anchor 这个概念是必备的，所以是得讲一下。
The object/background criterion and bounding box regression are defined with respect to a set of anchors.
Following \cite{lin2017feature}, we assign anchors with the same scale to each of the different pyramid levels. For detail information of the anchor setting, please refer to \cite{lin2017feature}.
% For every modulated layer, we attach a classification layer and a regression layer to make predict.
\iffalse
The loss function of stage 1 is:
\begin{equation}
    \mathcal{L}_1 = 
\end{equation}
\fi
% you need to say how we get the candidates. Faster R-CNN already says it.
%The generated proposes with top-K classification scores is send to stage2.
We use the top-$N$ ranked proposal regions for the refine stage.

\subsection{Adversarial dropout module}
%stage 1 的网络结构已经交代清楚了，就是一个FPN。和调制，和分类/回归层。那么stage的网络结构也应该交代清楚：roi align + 特征融合 + 对抗 + 分类/回归层。
\label{sec:stage2}
% 首先你要讲一下stage2在全局中的作用。
The refine stage aims to select the target from candidate proposals.
% 或许该讲一下stage2的输入包括：真实目标特征+候选区域。
% The input of stage 2 consists of: (1) The target feature is $f_{z} \in \mathbb R ^{256 \times 7 \times 7}$. (2) The candidate boxes generated from stage 1.
% Stage 2 compose of a feature merge module, a adversarial dropout module, a classifier layer $h^{cls}$ and a regression layer $h^{reg}$. 
Features of these candidate proposals are cropped from the search feature pyramid $F_{x}$ using RoIAlign \cite{he2017mask}, and then fused with the target feature $f_{z}$:
\begin{equation}
    \mathcal{X} = \mathcal{R}(b, F_{x}) \odot f_{z},
\end{equation}
where $\mathcal{R}$ represents the RoIAlign, $\odot$ represents the element-wise multiplication, $b$ represents an RoI in candidate proposals and $\mathcal{X}$ represents the fused feature of $b$.
%where $x' \in \mathbb R ^{256 \times 7 \times 7}$.
%$x' \in \mathbb R ^{256 \times 7 \times 7}$ is the feature of an RoI cropped from unmodulated feature pyramid using RoIAlign \cite{he2017mask}.
%The merged feature of a candidate target is:$x = x' \odot x_0$, where $\odot$ represents the element-wise multiplication. $x$ is the merged feature of that RoI.
% Maybe you need to say why you do the merge again.
% The modulation in stage 1 and the feature merge in stage 2 play different part in the tracking process. The modulation aims to detect the similar appearance in the whole image. The

>>>>

\chapter{暹罗跟踪者的端到端时间特征集合}\label{chap:end}

\section{摘要}
尽管暹罗网络已经证明了对象跟踪性能的显着提高，但是如何在暹罗跟踪器中利用时间信息尚未得到广泛研究。在本文中，我们介绍了一种新颖的暹罗跟踪体系结构，该体系结构配备了一个时间聚合模块，该模块通过聚合来自相邻帧的时间信息来改善每帧的特征。这种时间融合策略使暹罗跟踪器可以处理较差的对象外观，例如运动模糊，遮挡，\ textit {etc}。此外，我们在暹罗网络中整合了对抗性辍学模块，以端到端的方式计算出具有歧视性的目标特征。全面的实验表明，所提出的跟踪器的性能优于最新的跟踪器。

\section{简介}
\label{sec:intro}
视觉对象跟踪是估计视频序列每一帧中任意目标状态的任务。 
%Recently, siamese network [] is introduced into visual tracking community, which has already been applied in many applications [].
%The key idea of siamese tracking architecture is, the target and the search image share the same feature extractor, then use correlation to tell the target position.
最近，暹罗网络已经证明了对象跟踪性能的显着提高。
%However, sometimes the performance is bad 
但是，由于视频（图\ref{fig:visulization})中的对象外观变差，例如运动模糊，遮挡等，
因此学习到的通用表示可能没有那么大的判别力。
研究人员尝试了不同的方法来改进特征表示。
例如，
%RASNet \cite{wang2018learning} explores diverse attention mechanisms to adapt the offline learned feature representations to a specific tracking target.
SA-Siam \cite{he2018twofold} 分别训练两个分支，以保持语义/外观特征的异构性。
在 DaSiamRPN \cite{zhu2018distractor}中，设计了一个新颖的可感知干扰物的增量学习模块，该模块可以有效地将常规嵌入转移到当前视频域，并在推理过程中增量捕获目标外观变化。
SiamRPN++ \cite{SiamRPN++} 引入了一种简单而有效的采样策略，以更强大的深度架构来驱动暹罗跟踪器。
这些努力产生了一些影响，并提高了最新的准确性。
%These improvements are useful.
%However, all these effort ignores a important problem: they ignore to merge the inter-frame feature during the training phase.
%One important solution is use the temporal information.
%The use of temporal information is important because, when one frame is bad, the adjusting frame can be used. While several method trying to use the temporal information, the method is naive.
%(The bug is, I cannot find any temporal information used in siamese trackers. (I cannot believe it!!! Check it again.--Checked)) For example, A use a time memory to store the appearance information. B use a simple feature average during test. C use history positional information to predict the object position in current frame. However, all these method cannot handle the temporal information during training, which lead to sub-optimal result. To solve this problem, 
但是，上述所有暹罗算法都基于仅从当前帧裁剪的特征执行跟踪，这限制了暹罗跟踪器的功能。

\begin{figure}[t]
    \centering
    \includegraphics[width=1.0\textwidth]{Img/end/visulization.pdf}
    \caption{将我们的方法与SiamMask和SiamFCv2进行比较。示例框架来自GOT-10k测试装置。与现有方法相比，我们的方法可有效处理不良的对象外观。}
    \label{fig:visulization}
\end{figure}

实际上，视频具有关于目标的丰富信息，并且这种时间信息是视频理解和跟踪的重要基础。
例如，在视频对象检测中，FGFA \cite{zhu2017flow}在特征级别上利用了时间一致性。它通过沿运动路径聚集附近的特征来改善每帧特征，从而提高了视频识别精度。
在视频对象分割中，STCNN \cite{xu2019spatiotemporal}引入了时间相干模块，该模块着重于捕获动态外观和运动提示以提供对象分割的指导。
在基于区分性相关过滤器的对象跟踪中，FlowTrack \cite{zhu2018end} 专注于利用连续帧中的丰富流信息来改善特征表示和跟踪精度。
但是，如何在暹罗跟踪器中利用时间信息尚未得到广泛研究。

\begin{figure*}[t]
    \centering
    \includegraphics[width=1.0\textwidth]{Img/end/net_v3.pdf}
    \caption{
    我们的两阶段SiamTFA概述。
    %At the first stage, a siamese FPN equipped with a temporal aggregation module provides features of the template image and the search image. Then the feature modulation module is used to merge the features and generate proposals.
    %proposals of the object given in the first-frame bounding box. 
    %At the second stage, 
    提案生成阶段旨在生成视觉上类似于给定模板目标的提案。精炼阶段旨在从候选提案中选择目标。}
    \label{fig:SiamTFA}
\end{figure*}

% key words: temporal modeling, model the temporal information, temporal fusion, inter-frame information, improve the feature representation, temporal aggregation, poor object appearance
在本文中，我们旨在充分利用暹罗跟踪器中的时间信息。
%(We introduce a novel siamese tracking architecture equipped with a temporal aggregation module to make full use of inter-frame information.)
%(In this work, to deal with the issues raised above, we propose a novel tracker to aggregate features of adjacent frames by ...)
%(In this paper, we develop an end-to-end temporal aggregation module in siamese architecture to utilize both the power of siamese trackers and the inter-frame information.)
我们介绍了一种新颖的暹罗跟踪体系结构，该体系结构配备了时间聚合模块，该模块通过聚合相邻帧中的特征来改善每帧的特征。
这种时间融合策略使暹罗跟踪器能够处理不良的对象外观，例如运动模糊，遮挡等。
为此，我们在暹罗网络的主干中沿时间维度 \cite{lin2019tsm} 移动频道。
请注意，由于视频运动 \cite{zhu2017flow}，同一对象的特征通常不会在整个帧上在空间上对齐，因此仅对残差层 \cite{lin2019tsm} 进行时间平移，以保持暹罗语的空间特征学习能力追踪器。
与其他时间融合方法 \cite{tao2016siamese, gladh2016deep}不同，引用的方法能够在大规模数据集上进行端到端的训练。
建议的时间聚合模块在暹罗网络中进行了端到端的培训。
%The proposed temporal aggregation module is trained end-to-end in the siamese network.
%(This module enables our module to be trained end-to-end on large-scale datasets.)
此外，我们的时间融合方法易于实施，而无需更改暹罗跟踪架构或使用光流 \cite{zhu2018end}。

%improve the generalization ability on bad object.
%Our insight is that, if we only rely on the traditional training method, the bad image in the training data will be over wheeled by the easy cases. So the tracker shows bad performance when meeting with bad image during testing. To solve this problem, we take advantage of the recent progress in adversarial learning to increase the robustness of object features.
%Our method employs adversarial dropout to increase the robustness of object features. 
%注意，由于该模块在文章中占据次要位置，所以不应该写目前方法存在的缺点，而应该直接写用了这个模块后起到的作用。
%感觉概括性的优点不太好想，所以可以多些几句实现细节。这就要求我们弄懂代码原理。
为了提高目标功能的鲁棒性，我们在暹罗跟踪网络中进一步整合了一个对战辍学 \cite{park2018adversarial} 模块。
% add adversarial dropout to enforce the tracker to learn difficult cases. 
% (We further propose a adversarial training module to enforce the tracker to learn difficult cases. The motivation is that ... This is achieved by computing the adversarial masks based on diversity maximum. This simple form of feature selection improves the discrimination power of the tracker.)
%Specifically, we calculate the diversity of two dropouts, and make the loss max to learn the difficult dropout mask.
具体来说，我们首先根据散度最大值预测对抗性辍学蒙版。
然后，我们旨在最大程度地减少随机删除的特征和对抗删除的特征之间的差异。
%The effect of this module can be interpreted from both the dropout and from the adversarial training perspectives.
该模块具有辍学和对抗训练的优势：辍学使我们的暹罗网络在训练过程中随机断开神经单元，以防止目标特征的共同适应；而对抗训练则使我们的跟踪器学习困难的情况。

@@

\section{建议的方法}
\label{sec:method}
%应该提及我们的跟踪器的损失函数包括：对抗性损失，加上常规跟踪损失。
%In this section, we will introduce the proposed tracking method, SiamTFA (Fig. \ref{fig:SiamTFA}). 
%The main feature is:
%(1) A strong backbone. Use FPN and new-proposed feature modulation.
%(2) Equipped with 2 useful module: temporal aggregation module and adversarial dropout module to improve the robustness of features.
%In the following, three sub-section will be introduced: (1) Overview of tracking (2) Temporal aggregation module (3) Adversarial dropout module.
%网络结构怎么描述？可以参考ATOM。
%Our SiamTFA bases on a strong feature extractor -- FPN.
%We insert our temporal aggregation module in the backbone. Details of this module will be introduced at sec 3.2.
%Be robust to object size.
%FPN: handle different object size.
%modulator vector: handle different template object size.
%xcorr depth-wise: stage1 merge.
%element wise product: stage2 merge
% 介绍输入
%The input of the network is ... We use notations ... to denote ..., respectively. ... has a size of ...
%SiamTFA is composed of ... and ...
%Inspired by the great success of siamese trackers \cite{SiamRPN++, Wang2018SiamMask}, we also construct our SiamTFA based on the siamese architecture.
在本节中，我们将介绍拟议的基于暹罗体系结构的跟踪方法，即SiamTFA（图\ref{fig:SiamTFA}），其灵感来自暹罗跟踪器 \cite{SiamRPN++, Wang2018SiamMask}的巨大成功。
具体而言，SiamTFA将图像对作为输入，包括模板图像和搜索图像。模板图像是根据地面真实边界框从初始帧裁剪的图像块。搜索图像是视频其余部分中的一整帧。两个输入共享相同的特征提取器和参数。
受两阶段检测范例 \cite{ren2015faster}成功的启发，我们的暹罗跟踪器也是一种两阶段方法。第一阶段旨在生成在视觉上类似于给定模板目标的建议。在这个阶段，我们介绍一个时间聚合模块
%(Fig. \ref{fig:TSM}) 
增强时间信息（请参见\ref{sec:stage1})。第二阶段旨在从候选提案中确定目标。
% select the target from candidate proposals. 
在这一阶段，我们插入一个对抗性辍学模块以学习更强大的功能（第 \ref{sec:stage2}节）。

\subsection{临时汇总模块}
\label{sec:stage1}
% Note that 'stage1' and 'stage2' is a local term. You should introduce the global architecture which includes 'stage1' and 'stage2' first.
% You need to say something about ‘siamese' and the 'input'.
提案生成阶段包括3个组件：（1）特征提取器，（2）时间聚合模块和（3）特征调制模块。
% 需要综述三个模块在stage1中的作用。
特征提取器分别为搜索图像和模板图像生成搜索特征和模板特征。时间聚合模块被集成到特征提取器中以利用时间信息。特征调制模块合并搜索特征和模板特征以识别候选目标。

\textbf{特征提取器} 为了处理目标的比例变化，我们使用Res50-FPN \cite{lin2017feature} 作为特征提取器。
% You need to describe FPN here. What is FPN?
\textbf{F}eature \textbf{P}yramid \textbf{N}etwork (FPN) 利用深层卷积网络固有的多尺度金字塔层次结构来构建具有少量额外成本的特征金字塔。
我们的暹罗FPN将模板图像和搜索图像作为输入。对于搜索图像，FPN以完全卷积的方式在多个级别上输出按比例大小的特征图。
%The input of the feature extractor is an image pair consists of a template image and a search image. The search image is resized to min size 800. The template is cropped according to ground truth bounding box and resized into 400*400. According to the siamese architecture, the template/search image share the same parameters. 
%For the search image, we got 5 different features and they have strides of \{4, 8, 16, 32, 64\} pixels with respect to the input image. For template branch, we use the last layer of FPN with size 7*7. 
我们将搜索图像的输出表示为 $F_{x} = \{f_{x}^i\}_{i=1:5}$，并注意它们的步幅为 \{4, 8, 16, 32, 64\} 相对于输入搜索图像为像素。
对于模板图像，我们使用 FPN 最后阶段的输出作为模板特征，其空间大小为 $7 \times 7$。
%Different from traditional trackers, our template/search features have temporal information. The reason is because we insert the temporal shift module into the backbone, which will be introduced next.

\textbf{临时汇总模块}
%Different from traditional trackers, we use the rich information about the same object instance by 
最受欢迎的暹罗跟踪器 \cite{SiamRPN++, Wang2018SiamMask} 使用静止图像进行预测。% However, tracking on single frame generates unstable results and fails when appearance is pool \cite{zhu2017flow}. 
这限制了这些暹罗跟踪器的能力。
一方面，单帧跟踪会产生不稳定的结果，并且在外观不佳时会失败（图 \ref{fig:visulization})；另一方面，
时间相邻帧可以提供有关目标的更多信息。
%the video has rich information about the target. 
因此，我们旨在通过汇总相邻帧的特征来改善每帧特征。
具体来说，我们将一个时间聚合模块插入特征提取器的最后一个阶段。
% We have to cite TSM, because we use this idea.
为了对时间信息进行建模，一批图像是同一视频中的几个相邻帧，并按时间排序，因此我们可以将批次维度视为时间维度。假设特征提取器最后阶段的特征映射为 $f \in \mathbb R ^ {T \times C \times H \times W}$。
对于每次 $t \leq T$，我们首先将特征 $f^t \in \mathbb R ^ {C \times H \times W}$ 沿通道维度分为三部分：$f_{1:K}^t \in \mathbb R ^ {K \times H \times W}$，$f_{(K+1):2K}^t \in \mathbb R ^ {K \times H \times W}$ 和 $f_{(2K+1):C}^t \in \mathbb R ^ {(C-2K) \times H \times W}$。
然后，按照 \cite{lin2019tsm}沿时间维度移动通道：
% Then The aggregated function at time $t$ is:
\begin{equation}
    f_{agg}^t = \mathcal{C}(f_{{1:K}}^{t-1}, f_{(K+1):2K}^{t+1}, f_{(2K+1):C}^{t}),
\end{equation}
其中 $\mathcal{C}(\cdot)$ 是串联操作。根据 \cite{lin2019tsm}，移位操作仅在残差层执行，以保留暹罗跟踪器的空间特征学习能力。
请注意，聚合特征 $f_{agg}^t$ 具有与 $f^t$相同的形状，因此我们可以将此模块直接插入到主干中，而无需更改网络的其他部分。
而且，此操作仅需要进行数据移动，因此它在计算上是免费的，并且可以端到端进行训练。
% Say the effect of this module.
%After performing such channel fusion, rich target information in adjacent frames can be aggregated into the current frame. For example, if the current frame is blurred, target information that is not blurred in adjacent frames can be used.

@@

\textbf{功能调制模块} 在获得模板特征 $f_{z}$ 和搜索特征金字塔 $F_{x} = \{f_{x}^i\}_{i=1:5}$之后，被调制以生成特定于目标的特征。
具体而言，使用全局平均池生成生成调制矢量 $f_{avg}$ 从 $f_{z}$，该全局平均池携带目标特定的外观信息。
%The search feature pyramid is $F = \{f_1, f_2, f_3\}$. 
%For $f_{x}^{i} \in F_{x}$, t
调制特征金字塔 $F_{mod} = \{f_{mod}^i\}_{i=1:5}$ 生成如下：
\begin{equation}
    f_{mod}^i = \mathcal{M}(f_{avg}, f^i_x),
\end{equation}
其中 $\mathcal M(\cdot)$ 是深度相关 \cite{SiamRPN++}。
%So we get the modulated feature pyramid $F_{mod} = \{f_{mod}^i\}_{i=1:5}$. 
%Then we predict proposals on $F_{mod}$.
每个调制的特征图都馈入两个同级的全连接层中-通道尺寸为4$k$的盒子回归层和通道尺寸为2$k$的盒子分类层，其中 $k$ 是每个位置的最大建议数量。
% anchor 这个概念是必备的，所以是得讲一下。
相对于一组锚定义了对象/背景标准和边界框回归。
在 \cite{lin2017feature}之后，我们将具有相同比例的锚分配给每个不同的金字塔等级。有关锚点设置的详细信息，请参阅 \cite{lin2017feature}。
% For every modulated layer, we attach a classification layer and a regression layer to make predict.
\iffalse
The loss function of stage 1 is:
\begin{equation}
    \mathcal{L}_1 = 
\end{equation}
\fi
% you need to say how we get the candidates. Faster R-CNN already says it.
%The generated proposes with top-K classification scores is send to stage2.
在优化阶段，我们使用排名靠前的$N$ 个提案区域。

\subsection{对抗 dropout 模块}
%stage 1 的网络结构已经交代清楚了，就是一个FPN。和调制，和分类/回归层。那么stage的网络结构也应该交代清楚：roi align + 特征融合 + 对抗 + 分类/回归层。
\label{sec:stage2}
% 首先你要讲一下stage2在全局中的作用。
优化阶段旨在从候选提案中选择目标。
% 或许该讲一下stage2的输入包括：真实目标特征+候选区域。
% The input of stage 2 consists of: (1) The target feature is $f_{z} \in \mathbb R ^{256 \times 7 \times 7}$. (2) The candidate boxes generated from stage 1.
% Stage 2 compose of a feature merge module, a adversarial dropout module, a classifier layer $h^{cls}$ and a regression layer $h^{reg}$. 
这些候选投标的特征是使用RoIAlign \cite{he2017mask} 从搜索特征金字塔 $F_{x}$ 中裁剪出来的，然后与目标特征 $f_{z}$融合在一起：
\begin{equation}
    \mathcal{X} = \mathcal{R}(b, F_{x}) \odot f_{z},
\end{equation}
其中 $\mathcal{R}$表示RoIAlign，$\odot$表示按元素相乘，$b$表示候选投标书中的RoI，$\mathcal{X}$表示$b$的融合特征。
%where $x' \in \mathbb R ^{256 \times 7 \times 7}$.
%$x' \in \mathbb R ^{256 \times 7 \times 7}$ is the feature of an RoI cropped from unmodulated feature pyramid using RoIAlign \cite{he2017mask}.
%The merged feature of a candidate target is:$x = x' \odot x_0$, where $\odot$ represents the element-wise multiplication. $x$ is the merged feature of that RoI.
% Maybe you need to say why you do the merge again.
% The modulation in stage 1 and the feature merge in stage 2 play different part in the tracking process. The modulation aims to detect the similar appearance in the whole image. The
